Discrete Ordinates

### 2017-06-05 docprep/norris_phd_dissertation.tex
Finished draft of the thesis through the results
Wrote the abstract

\begin{ThesisAbstract}
This is the text for the abstract. Here, I explain what I did and how cool I am for doing it. Because I am awesome.
\end{ThesisAbstract}

@@

\begin{Vita}
Edward Norris graduated from Missouri University of Science and Technology in 2013 with a B.S. in both nuclear engineering and computer science, he is currently pursuing both a M.S. in computer science and a PhD in nuclear engineering. His PhD work is currently funded by a fellowship through the NRC.

@@

Edward was awarded the College of Engineering and Computing PhD Scholar award in 2017 for his academic achievements.

@@

After completing his PhD, he plans to take a one year postdoctorial fellowship position with the NNSA.

>>>>

\begin{ThesisAbstract}
This is the text for the abstract. Here, I explain what I did and how cool I am for doing it. Because I am awesome.

Computed tomography (CT) has become pervasive in medical diagnostics as improved imaging techniques and processing algorithms provide higher quality information to doctors. However, the exponentially increasing usage of CT has raised concerns regarding long term radiological risks.

\end{ThesisAbstract}

@@

\begin{Vita}
Edward Norris graduated from Missouri University of Science and Technology in 2013 with a B.S. in both nuclear engineering and computer science, he is currently pursuing both a M.S. in computer science and a PhD in nuclear engineering. His PhD work is currently funded by a fellowship through the NRC. Edward was awarded the College of Engineering and Computing PhD Scholar award in 2017 for his academic achievements.

@@

@@
